% !TeX root = ../OSN.tex

\subsection*{A. Real-World Datasets}
We thank the authors of \cite{kumar2016edge} who release the datasets online for research.
The real-world datasets used for evaluation are summarized in Table 2.
The listed networks are all directed. i.e. each edge ($u,v$) means that user
$u$ is expressing an opinion about user $v$. Each edge is associated with a
weight $W(u,v)$ representing the strength of opinion. The weights for all 
the networks are normalized in the range of [$-1$, $1$]. The meaning 
of each network is illustrated as follows:

\emph{\textbf{Bitcoin networks}}. As a cryptocurrency ussed for 
anonymous trading, Bitcoin is always accompanied with certain risk.
Therefore, users often rate the level of trust they have in others.
Based on such exchange, Bitcoin-OTC and Bitcoin-Alpha$^2$ are gatherd
on a scale between $-10$ and $10$. $-10$ means the person at that node 
may like be a fraudster, while $10$ means a person can be most trusted.
Thus, these two exchanges explicitly yield WSNs.

\emph{\textbf{Wikipedia RfA}} Wikipedia Requests for Adminship (RfA) 
network is a signed network among Wikipedia users where each 
edge ($u,v$) has a weight corresponding to the vote of user $u$
($-1$ for negative, 0 for neutral, and 1 for positive) towards user 
$v$ to become an administrator. To normalize this dataset in the
range of [$-1$, $1$]. An online sentiment engine is used to quantify
the strength of each score based on the intensity of the sentiment expressed 
in its explanation.

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\begin{table}[htbp]
\centering
\caption{Real-world datasets used for evaluation}
  \begin{tabular}{l|c|c|c|c}
  \toprule
  \textbf{Network}& \textbf{Vertices} & \textbf{Edges} & \textbf{Pos. Edges $\%$} & \textbf{Description of network edges} \\ \hline
  Bitcoin-Alpha         & 3,783 & 24,186 & $93\%$  & \tabincell{c}{Degree of trust or distrust \\ from Bitcoin user $u$ to $v$} \\ \hline
  Bitcoin-OTC           & 5,881 & 35,592 & $89\%$  & \tabincell{c}{Degree of trust or distrust \\ from Bitcoin user $u$ to $v$} \\ \hline
  Wikipedia RfA         & 9,654 & 104,554 & $83.7\%$  & \tabincell{c}{Degree of support or opposition \\ in Wikipedia administrator \\elections by $u$ to $v$} \\ \hline
  \end{tabular}
\end{table}

